Water Management

### 2020-02-24 Paper/paper.tex
changes as discussed

So the value of the control variable to be set is the one that maximizes both the utility of the current state plus (recursively) the value $V$ of the next state $s'$ which is discounted by a factor of $\beta$.

@@

	\begin{equation}
s = \left( \begin{array}{c}0\\...\\7\end{array}\right),\hspace{2mm}x = \left( \begin{array}{c}0\\...\\7\end{array}\right)
\end{equation}
% TODO Gibt es hier nicht eine mathematisch schönere Schreibweise um einen Vektor mit 1000 Einträgen darzustellen? (R hoch 1000/ R hoch n)
% TODO das scheint mir nicht so ganz korrekt zu sein. Meint ihr die Dimension?
Note that the maximum reservoir capacity is $7$ and $|s|=|x| = n = 1000$.

@@

	\item The diminishing margin utility of farmers lead to a decreasing gradient for the proposed irrigation amount with increasing water level.

@@

To do so, we ran our code 1000 times and put the resulting water levels into bins with the size of 0.1 each. % "the forward simulation" instead of "our code"? Außerdem laut code 500x statt 1000x

@@

A small $\beta$ ensures that high water levels at the end of one period are only available to a small extent in the next period. % Finde die Formulierung nicht so gut: Sie sind ja weiterhin voll verfügbar, aber eben in Zukunft weniger wert. Bzw das könnte man diskutieren.

@@

Using a $\sigma^2=2$ includes a mean of $\mu=-1.5$ in order for the mean to stay the same. % Würde das erste "mean of mu" rausnehmen oder spezifizieren -> mean of the underlying normal distribution

@@

Nevertheless one can say that the overall shape of a lognormal distribution is a feasible estimation for rainfall but for estimating whole years as periods the distribution might to be parameterized differently to fit actual rainfalls. % feasible -> sensible?

@@

%TODO improve this figure
\begin{figure}[h]
	\includegraphics[width=1\textwidth]{figures/results-evap-factor-2.3.eps}
	\caption{Evaporation multiplied by a factor of $2.3$ outweighs the rainfall in certain periods} %TODO 
	\label{fig:evap-factor-2.3}
\end{figure}

>>>>

So the value of the control variable to be set is the one that maximizes both the utility of the current state plus (recursively) the value $V$ of the next state $s'$ which is discounted by a factor of $\beta$. 
%TODO hier noch auf die Definition von beta eingehen? Was ist beta und warum ist das relevant?

@@

	\begin{equation}
s = \left( \begin{array}{c}0\\...\\7\end{array}\right),\hspace{2mm}x = \left( \begin{array}{c}0\\...\\7\end{array}\right)
\end{equation}
Note that the maximum reservoir capacity is $7$ and $s, x \in R^{1000}$.

@@

	\item As long as the discount factor $\beta$ is larger than 0, the water within the reservoir has a value in the next period for both recreational users and farmers. Due to this effect, saving waters makes sense and leads to a decreasing gradient for the proposed irrigation amount with increasing water level.

@@

To do so, we ran our code 1000 times (in specific, the forward simulation) and put the resulting water levels into bins with the size of 0.1 each. 

@@

A small $\beta$ ensures that high water levels at the end of one period are only available to a small extent in the next period. 
%TODO Finde die Formulierung nicht so gut: Sie sind ja weiterhin voll verfügbar, aber eben in Zukunft weniger wert. Bzw das könnte man diskutieren.

@@

Using a $\sigma^2=2$ includes setting $\mu=-1.5$ in order for the mean to stay the same.

@@

Nevertheless one can say that the overall shape of a lognormal distribution is a sensible estimation for rainfall but for estimating whole years as periods the distribution might to be parameterized differently to fit actual rainfalls. 

@@

%TODO improve this figure
\begin{figure}[h]
	\includegraphics[width=1\textwidth]{figures/results-evap-factor-2-3.eps}
	\caption{Evaporation multiplied by a factor of $2.3$ outweighs the rainfall in certain periods} %TODO 
	\label{fig:evap-factor-2.3}
\end{figure}
